Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-10-20 SubGenome Analysis.Rmd
Added fit line

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = abs(foldChange))) +
  scale_color_gradient(low = "blue", high = "red") +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  xlim(0,100) +
  ylim(0,100) +
  labs(
    title = paste0("Scatterplot of isoform counts for gene pair(s).\nExcludes ",n," outlier, alpha=.1, foldchange in log2."),
    x = "Isoform Counts for Maize1 Gene",
    y = "Isoform Counts for Maize2 Gene"
  )
plot(plot)
```

@@

@@

>>>>

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = abs(foldChange))) +
  scale_color_gradient(low = "blue", high = "red") +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  xlim(0,100) +
  ylim(0,100) +
  labs(
    title = paste0("Scatterplot of isoform counts for gene pair(s).\nExcludes ",n," outlier, alpha=.1, foldchange in log2, blue=lm fit."),
    x = "Isoform Counts for Maize1 Gene",
    y = "Isoform Counts for Maize2 Gene"
  ) + 
  annotate("text",x=85,y=20, label=paste("Pearson Cor = ", round(cor(data$Value_maize1, data$Value_maize2, method = c("pearson")),2)))
plot(plot)
```

@@

```{r include=FALSE}
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.expression.sample.avg, by=c("Maize1"="geneID")) %>%
  inner_join(maize.expression.sample.avg, by=c("Maize2"="geneID", "Sample"="Sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "FPKM_maize1"
names(data)[5] <- "FPKM_maize2"

data$foldChange_expr <- log2(data$FPKM_maize1) - log2(data$FPKM_maize2)
data$foldChange_abun <- log2(data$dNSAF_maize1) - log2(data$dNSAF_maize2)
```

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('./Data/Images/Top fold-change genes.png')
```
